Super vs fficient absorption of light by spherical nanoparticles

### 2015-07-13 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-aem.tex
Fig 3 is now recalculated

@@

A noticeable feature of Fig.~\ref{fig:spectra} (c) is an almost flat
top of the electric dipole resonance. (TODO add some explanation, why
it flat? Any ideas?  - not really, maybe there are two different
dipole "types", and we see their interference?)

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for R=36 nm (a,c) and
      ``super'' (b,d) designs in E-k  (a-b) and H-k (c-d) planes. 
      \label{fig:field}
    }%
  }
\end{figure}
%
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a super-absorbing design with
$R=63$~nm.  We set different scale for these two designs so that black
circles that denote outer boundary are plotted to be the same size.
We also plot streamlines of the Poynting vector which characterize
energy flow. For the effective design of the absorber, the power from
a large cross-sectional area flows into the particle.  In case of
super-absorption regime, we observe power flow vortices, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.

>>>>

Another approach for an ideal absorber was given in a recent work by
Grigoriev et al.~\cite{Grigoriev-2015}. However, they considered only
a dipole approximation, the final value for our range of particle
sizes is very close to the dipole limit predicted with
Tribelsky~\cite{Tribelsky-2011}.  Thus, such super-absorption designs
correspond to single mode limit.  At the same time, Grigoriev et
al.~\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from predefined materials. However, in case of
$Si$ and $Ag$ materials and size parameter from our best design, their
equation gives a complex value for core material filling factor, which
is not practical for any experimental realisations.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/Fig1}%
    \caption{ Shematic view of the simulated $Si/Ag/Si$ particle. 
      \label{fig:geom}
    }%
  }
\end{figure}

@@

A noticeable feature of Fig.~\ref{fig:spectra}~(c) is an almost flat
top of the electric dipole resonance.
% maybe there are two different dipole "types", and we see their
% interference?
To answer this question we need to look at the internal coefficients of each layer.
There is no interference between multipoles - they are orthogonal modes ;-)
 Whereas resonant responses
of other designs originate from coupling of incident plane wave with
the corresponding multipole, it is not the case for the design with
$R=81$~nm. Here, the particle is mostly composed from the $Si$ outer
shell, that give enough volume for $\tilde{b}_2$.  Dipole response
comes from the small inner part of the sphere and can not be directly
excited with the incident wave.  It takes the power from the
surrounding $\tilde{b}_2$ mode and very soon it reaches the
fundamental limit for absorption.  This way, we can observe a flat top
for the $\tilde{a}_1$ response accompanied with a significant value of
$\tilde{b}_2$.  Our suggestion is indirectly proved by the reduced
width of the $\tilde{b}_2$ resonance compared to other quadrupole
responses.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for R=36 nm (a,c) and
      ``super'' (b,d) designs in E-k  (a-b) and H-k (c-d) planes. 
      \label{fig:field}
    }%
  }
\end{figure}
%
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a super-absorbing design with
$R=63$~nm.  We set different scale for these two designs so that black
circles that denote outer boundary are plotted to be the same size.
We also plot streamlines of the Poynting vector which characterize
energy flow. For the effective design of the absorber, the power from
a large cross-sectional area flows into the particle.  In case of
super-absorption regime, we observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a super-design is obvious:
spatial distribution of the electric field is not uniform inside the
particle and the share of the volume with high absorption rate in the
vortices do not compensate low absorption efficiency in the regions
with small electric field ( absorbed power is expressed as $P_{\rm
  abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)
